Improved Quasi-Static Methods for Time-Dependent Neutron Diffusion and Implementation in Rattlesnake

### 2017-03-07 doc/Defense/Defense_Prince.tex
Defense: Changes after mock presentation

@@

%-------------------------------------------------------------------
\begin{frame}{Bottom Line Up Front}

@@

\begin{block}{Objectives}
\begin{itemize}
\item Establish IQS performance for various nonlinear iteration techniques
\item Validate time step convergence for IQS with high order discretization schemes
\item Apply IQS to multiphysics simulations
\end{itemize}
\end{block}

\begin{block}{Conclusions}
\begin{itemize}
\item IQS is an effective method for reducing computational expense of transient reactor simulations
\item The IQS uniqueness criteria is important to keep consistent through nonlinear iteration and accurate precursor evaluation
\item IQS demonstrates proper error convergence up through fourth order methods and shows impressive performance with time adaptation
\item IQS implementation in Rattlesnake was effective and greatly reduced computational expense in TREAT simulations
\end{itemize}
\end{block}

@@

\begin{block}{}
\begin{itemize}
\item Direct time discretization of these equations is known as "implicit discretization"
\item These equations are particularly stiff due to the large value of $v$
\item Implicit schemes are necessary with many points of time discretization (time steps)
\end{itemize}
\end{block}

@@

\begin{block}{Factorization}
Point reactor kinetics involve factorizing flux into space and time dependent components:
\be
\phi(\vr,E,t) = \phi(\vr,E)\times p(t)
\ee
\end{block}

@@

\begin{block}{Uniqueness of the factorization}
In order to impose uniqueness of the factorization, one requires:
\[
\tcp{K_0} = \sum_{g=1}^G\left(\phi^{*g},\frac{1}{v^g}\varphi^g\right)= constant
\]
\end{block}

@@

\small \be
\frac{\rho-\bar{\beta}}{\Lambda}=
\frac{ \sum_{g=1}^G \left(\phi^{*g},\sum_{g'=1}^G\frac{\chi_p^g}{\keff} \nu_p^{g'} \Sigma_f^{g'}\varphi^{g'} + \sum_{g'\neq g}^G\Sigma_s^{g'\to g} \varphi^{g'} -\left( -\div D^g \grad  + \Sigma_r^g \right)\varphi^g\right)}
{\sum_{g=1}^G \left(\phi^{*g},\frac{1}{v^g}\varphi^g\right)}
\ee \normalsize
%%
\be
\frac{\bar{\beta}}{\Lambda}=\sum_{i=1}^I\frac{\bar{\beta}_i}{\Lambda}=\frac{1}{\keff}
\frac{\sum_{i=1}^I\sum_{g=1}^G(\phi^{*g}, \beta_i\nu^{g} \Sigma_f^g \varphi^{g})}
{\sum_{g=1}^G \left(\phi^{*g},\frac{1}{v^g}\varphi^g\right)}
\ee
%%
\be
\bar{\lambda}_i=\frac{\sum_{g=1}^G(\phi^{*g},\chi_{d,i}^g\lambda_i C_i)}{\sum_{g=1}^G(\phi^{*g},\chi_{d,i}^gC_i)}
\ee

@@

%-------------------------------------------------------------------
\begin{frame}{Quasi-Static Process}
\vspace{-2mm}

@@

\begin{block}{Variable time discretization}
\begin{itemize}
\item To ensure stability, only implicit discretization schemes
\item PRKE error kept constant, so either very small time steps or adaptive methods
\item Schemes for shape include:
\begin{itemize}
\item Implicit Euler
\item Crank-Nicolson
\item Backward Difference Formulae (DDF)
\item Singly-Diagonally-Implicit Runge-Kutta (SDIRK)
\end{itemize}
\end{itemize}
\end{block}

@@

\begin{block}{Factorization leads to a nonlinear system}
The \tcr{amplitude} and \tcb{shape} equations form a system of nonlinear coupled equations: 
\ben
\item Coefficients appearing in the \tcr{PRKE}'s depend upon the \tcb{shape} solution
\item \tcb{Shape} equation has a kernel dependent on \tcr{amplitude} and its derivative  
\item Delayed neutron source term is scaled by the \tcr{amplitude}
\een
\end{block}

@@

@@

%-------------------------------------------------------------------
\begin{frame}{Relevant convergence criteria}

\begin{block}{IQS convergence criteria}
\begin{itemize}
\item \tcb{Shape} based convergence:
\be
\frac{\text{max}\left|\varphi_{n}^{(k+1)} - \varphi_{n}^{(k)}\right|}{\text{max}\left|\varphi_{n}^{(k+1)}\right|} < \epsilon_{\varphi}
\ee 
\be
\frac{\norm{\varphi_{n}^{(k+1)} - \varphi_{n}^{(k)}}}{\norm{\varphi_{n}^{(k+1)}}} < \epsilon_{\varphi}
\ee

@@

\item \tcr{Amplitude} based:
\be 
p_n^{k+1} - p_n^{k} < \epsilon_p
\ee

@@

%\begin{block}{IQS P-C Linearizes the System}
IQS P-C linearizes the system and avoids iterations on the \tcb{shape}: 
\ben
\item Evaluate multigroup diffusion equation to get predicted flux $\phi_{n+1}^{g,\tcr{pred}}$
\item Scale predicted flux to obtain \tcb{shape}:
\[
\tcb{\varphi^{g}_{n+1}} = \phi_{n+1}^{g,\tcr{pred}} \frac{\sum_{g=1}^G\left(\phi^{*g},\frac{1}{v^g}\phi ^g_{0}\right)}{\sum_{g=1}^G \left(\phi^{*g},\frac{1}{v^g}\phi_{n+1}^{g,\tcr{pred}}\right)} = \phi_{n+1}^{g,\tcr{pred}} \frac{\tcp{K_0}}{\tcp{K_{n+1}}}
\]
\item Compute PRKE parameters at $t_{n+1}$
\item Evaluate PRKE along micro step using interpolated parameters to obtain $\tcr{p_{n+1}}$
\item Scale $\tcb{\varphi^{g}_{n+1}}$ to obtain corrected flux:
\[
\phi_{n+1}^{g,\tcr{corr}} = \tcr{p_{n+1}} \times \tcb{\varphi^{g}_{n+1}}
\]
\een

 Advantage: No IQS nonlinear iteration is necessary \\
 Disadvantage: Assumes $\sum_{g=1}^G\left(\phi^{*g},\frac{1}{v^g}\varphi^g_{n+1}\right)$ is inherently constant \\

@@

@@

\begin{block}{Solution Process with IQS}

@@

%-------------------------------------------------------------------
\begin{frame}{Treatment of delayed neutron precursors}

\begin{block}{Solution vector treatment}
The system of equations for flux/shape and precursors can be solved as a coupled system:
\be
\frac{\partial}{\partial t} \begin{bmatrix} \tcb{\varphi} \\ C \end{bmatrix}
=
\begin{bmatrix} A & \lambda \\ \nu\Sigma_f \tcr{p} & -\lambda \end{bmatrix}
\begin{bmatrix} \tcb{\varphi} \\ C \end{bmatrix}
\ee
This is unnecessarily expensive and memory intensive because the precursor equation is an ODE
\end{block}

\begin{block}{Precursor Evaluation Using Theta Method Time Discretization}
The precursor ODE can be integrated in time using the theta method:
\be
C^{n+1} = \frac{1-(1-\theta)\Delta t\lambda}{1+\theta\Delta t\lambda}C^n + \frac{(1-\theta)\Delta t \beta}{1+\theta\Delta t\lambda}(\nu\Sigma_f\varphi)^n p^n +  \frac{\theta\Delta t \beta}{1+\theta\Delta t\lambda}(\nu\Sigma_f\varphi)^{n+1} p^{n+1}
\ee
Where this equation can be plugged into the time discretization of the shape equation
\end{block}

%-------------------------------------------------------------------
\begin{frame}{Semi-analytical treatment of delayed neutron precursors}

\begin{block}{Analytical Precursor Integration}
For IQS, the profile for the flux is very accurately defined because of the small micro-step PRKE evaluation. So the precursor integration can be represented semi-analytically:
\be
C^{n+1} = C^n e^{-\lambda \Delta t} + \left(\hat{a}_2 (\nu\Sigma_f\varphi)^{n+1}+\hat{a}_1 (\nu\Sigma_f\varphi)^n\right)\beta
\label{eq:dnp_an}
\ee
With integration coefficients defined as:
\begin{align*}
&\hat{a}_1= \int_{t_n}^{t_{n+1}}\frac{t_{n+1}-t'}{\Delta t}p(t')e^{-\lambda(t_{n+1}-t')}dt' \\
&\hat{a}_2 = \int_{t_n}^{t_{n+1}}\frac{t'-t_n}{\Delta t}p(t')e^{-\lambda(t_{n+1}-t')}dt'
\end{align*}
\end{block}

@@

%-------------------------------------------------------------------
\begin{frame}{Adiabatic heat-up with absorption cross-section feedback}

\begin{block}{Implemented Form}
Adiabatic heat-up and feedback that is used takes the following form:
\be
\rho c_p \frac{\partial T(\vec{r},t)}{\partial t} = \kappa_f \sum^G_{g=1}\Sigma_f^g \phi^g(\vec{r},t)
\ee
\be
\Sigma_a^{thermal}(\vec{r},t) = \Sigma_a^{thermal}(\vec{r},0)\left[1+\gamma\left(\sqrt{T}-\sqrt{T_0}\right)\right]
\ee
\end{block}

\begin{block}{Analytical temperature integration with IQS}
Similar to the precursor evaluation:
\be
T^{n+1} = T^n + \frac{\kappa_f}{\rho c_p} \left(a_2 \varphi^{n+1} + a_1 \varphi^{n}\right)
\label{eq:temp_an}
\ee
\be
a_1 = \int_{t_n}^{t_{n+1}}\left(\frac{t_{n+1}-t'}{\Delta t}\right)p(t')dt'
\label{eq:a1}
\ee
\be
a_2 = \int_{t_n}^{t_{n+1}}\left(\frac{t'-t_n}{\Delta t}\right)p(t')dt'
\label{eq:a2}
\ee
\end{block}

@@

\begin{block}{Solution Methods}
\begin{multicols}{2}
\begin{enumerate}
\item Implicit Discretization
\begin{itemize}
\item Precursor variable coupling
\item Theta precursor elimination
\item Analytical precursor elimination
\end{itemize}
\item IQS
\begin{itemize}
\item Precursor variable coupling
\item Theta precursor elimination
\item Analytical precursor elimination
\end{itemize}
\item IQS P-C
\begin{itemize}
\item Theta precursor elimination
\item Analytical precursor elimination
\end{itemize}
\item PRKE
\begin{itemize}
\item Parameter calculation using initial flux
\item Parameter calculation using flux calculated at various time steps
\end{itemize}
\end{enumerate}
\end{multicols}
\end{block}

@@

@@

\begin{columns}
\column{\dimexpr\paperwidth-10pt}
\begin{figure}
\includegraphics[width=0.5\linewidth]{figures/1D_conv_Rat.png}
\includegraphics[width=0.5\linewidth]{figures/1D_conv_lin.png}
\end{figure}
\end{columns}

@@

%-------------------------------------------------------------------
\begin{frame}{Transient-15 Results}

\begin{block}{Accuracy and Runtime}
\begin{center}
\resizebox{\linewidth}{!}{
\begin{tabular}{|l|ccccccc|}
\hline
 & No.	& Max &	Time at Max &	Max Average &	\% Increase &	Max Power & Linear	\\
Method & of Steps &	Power (W) &	Power (s) &	Temperature (K) & Runtime$^*$ & Error & Iterations \\
\hline
Baseline 			& 3000 	& 3.5039e+08 & 1.901 & 371 &	---		&	---		 & ---		\\
Implicit Dis. 		& 300 	& 3.5011e+08 & 1.90  & 371 &	---		&	7.875e-4 & 41020	\\
IQS 				& 300	& 3.5036e+08 & 1.90  & 371 & -11.9\%	&	8.385e-5 & 23949	\\
IQS (5 updates) 	& 300 	& 3.5040e+08 & 1.90  & 371 &  49.7\%	&	3.687e-5 & 24035	\\
IQS P-C 			& 300 	& 3.5065e+08 & 1.90  & 371 &  -2.1\%	&	7.527e-4 & 39020	\\
IQS P-C (5 updates) & 300 	& 3.5043e+08 & 1.90  & 371 &  26.5\%	&	1.227e-4 & 37866	\\
\hline
\end{tabular}
}
\end{center}
\vspace{-3mm}
$^*$ difference in runtime from implicit discretization 
\end{block}

@@

\begin{block}{IQS with Temperature Feedback}
\begin{itemize}
\item IQS was successfully implemented into the Rattlesnake/MOOSE framework
\item Incorporation of temperature into the quasi-static process significantly improved computational efficiency
\item Dynamical time scale analysis demonstrated proof-of-concept for variant time scales
\end{itemize}
\end{block}

@@

\begin{block}{Multiphysics}
Test IQS with other reactor physics, including:
\begin{itemize}
\item Thermal Hydraulics
\item Fuel Mechanics
\item Depletion
\end{itemize}
\end{block}

@@

>>>>

\newcommand{\backupbegin}{
   \newcounter{finalframe}
   \setcounter{finalframe}{\value{framenumber}}
}
\newcommand{\backupend}{
   \setcounter{framenumber}{\value{finalframe}}
}

@@

%-------------------------------------------------------------------
\begin{frame}{Objective}

@@

\begin{block}{What is IQS?}
\begin{itemize}
\item Transient neutronics method meant to minimize expensive diffusion evaluations
\item Non-approximately separates spatial variance and temporal power
\item Impetus is spatial variance doesn't change much in time, compared to powerb
\end{itemize}
\end{block}

\begin{block}{Objectives}
\begin{itemize}
\item Establish IQS performance for various nonlinear iteration techniques applied to transient neutronics
\item Validate time step convergence in transient neutronics problems for IQS with high order discretization schemes
\item Apply IQS to multiphysics simulations
\end{itemize}
\end{block}

%\begin{block}{Conclusions}
%\begin{itemize}
%\item IQS is an effective method for reducing computational expense of transient reactor simulations
%\item The IQS uniqueness criteria is important to keep consistent through nonlinear iteration and accurate precursor evaluation
%\item IQS demonstrates proper error convergence up through fourth order methods and shows impressive performance with time adaptation
%\item IQS implementation in Rattlesnake was effective and greatly reduced computational expense in TREAT simulations
%\end{itemize}
%\end{block}

@@

\begin{block}{}
\begin{itemize}
\item Direct time discretization of these equations is termed "implicit discretization"
\item These equations are particularly stiff due to the large value of $v$
\item Implicit schemes are necessary with many time steps
\end{itemize}
\end{block}

@@

\begin{block}{Factorization}
Point reactor kinetics involve factorizing flux into space and time dependent components:
\be
\phi^g(\vr,t) = \Phi^g(\vr)\times p(t)
\ee
\end{block}

@@

\begin{block}{Uniqueness of the factorization}
In order to impose uniqueness of the factorization, one requires:
\[
\tcp{K_0} = \sum_{g=1}^G\left(\phi^{*g},\frac{1}{v^g}\tcb{\varphi^g}\right)= constant
\]
\end{block}

@@

\small \be
\frac{\rho-\bar{\beta}}{\Lambda}=
\frac{ \sum_{g=1}^G \left(\phi^{*g},\sum_{g'=1}^G\frac{\chi_p^g}{\keff} \nu_p^{g'} \Sigma_f^{g'}\tcb{\varphi^{g'}} + \sum_{g'\neq g}^G\Sigma_s^{g'\to g} \tcb{\varphi^{g'}} -\left( -\div D^g \grad  + \Sigma_r^g \right)\tcb{\varphi^g}\right)}
{\sum_{g=1}^G \left(\phi^{*g},\frac{1}{v^g}\tcb{\varphi^g}\right)}
\ee \normalsize
%%
\be
\frac{\bar{\beta}}{\Lambda}=\sum_{i=1}^I\frac{\bar{\beta}_i}{\Lambda}=\frac{1}{\keff}
\frac{\sum_{i=1}^I\sum_{g=1}^G(\phi^{*g}, \beta_i\nu^{g} \Sigma_f^g \tcb{\varphi^{g}})}
{\sum_{g=1}^G \left(\phi^{*g},\frac{1}{v^g}\tcb{\varphi^g}\right)}
\ee
%%
\be
\bar{\lambda}_i=\frac{\sum_{g=1}^G(\phi^{*g},\chi_{d,i}^g\lambda_i C_i)}{\sum_{g=1}^G(\phi^{*g},\chi_{d,i}^gC_i)}
\ee

@@

%-------------------------------------------------------------------
\begin{frame}{Quasi-Static Process}
% \vspace{-2mm}

@@

%\begin{block}{Variable time discretization}
%\begin{itemize}
%\item To ensure stability, only implicit discretization schemes
%\item PRKE error kept constant, so either very small time steps or adaptive methods
%\item Schemes for shape include:
%\begin{itemize}
%\item Implicit Euler
%\item Crank-Nicolson
%\item Backward Difference Formulae (DDF)
%\item Singly-Diagonally-Implicit Runge-Kutta (SDIRK)
%\end{itemize}
%\end{itemize}
%\end{block}

@@

@@

\begin{block}{Fixed-Point Process}
\begin{figure}
\includegraphics[width=\linewidth]{figures/iqs_iter_proc.png}
\end{figure}
\end{block}

@@

%-------------------------------------------------------------------
\begin{frame}{Relevant Picard convergence criteria}

\begin{block}{IQS convergence criteria}
\begin{itemize}
\item \tcb{Shape} based convergence:
\be
\frac{\text{max}\left|\tcb{\varphi{n}^{(k+1)}} - \tcb{\varphi_{n}^{(k)}}\right|}{\text{max}\left|\tcb{\varphi{n}^{(k+1)}}\right|} < \epsilon_{\varphi}
\ee 
\be
\frac{\norm{\tcb{\varphi{n}^{(k+1)}} - \tcb{\varphi_{n}^{(k)}}}}{\norm{\tcb{\varphi_{n}^{(k+1)}}}} < \epsilon_{\varphi}
\ee

@@

\item \tcr{Amplitude} based:
\be 
\tcr{p_n^{k+1}} - \tcr{p_n^{k}} < \epsilon_p
\ee

@@

\begin{block}{IQS P-C Linearizes the System}
IQS P-C linearizes the system and avoids iterations on the \tcb{shape}: 
\ben
\item Evaluate multigroup diffusion equation to get predicted flux $\phi_{n+1}^{g,\tcr{pred}}$
\item Scale predicted flux to obtain \tcb{shape}:
\[
\tcb{\varphi^{g}_{n+1}} = \phi_{n+1}^{g,\tcr{pred}} \frac{\sum_{g=1}^G\left(\phi^{*g},\frac{1}{v^g}\phi ^g_{0}\right)}{\sum_{g=1}^G \left(\phi^{*g},\frac{1}{v^g}\phi_{n+1}^{g,\tcr{pred}}\right)} = \phi_{n+1}^{g,\tcr{pred}} \frac{\tcp{K_0}}{\tcp{K_{n+1}}}
\]
\item Compute PRKE parameters at $t_{n+1}$
\item Evaluate PRKE along micro step using interpolated parameters to obtain $\tcr{p_{n+1}}$
\item Scale $\tcb{\varphi^{g}_{n+1}}$ to obtain corrected flux:
\[
\phi_{n+1}^{g,\tcr{corr}} = \tcr{p_{n+1}} \times \tcb{\varphi^{g}_{n+1}}
\]
\een

 Advantage: No IQS nonlinear iteration is necessary \\
 Disadvantage: Assumes $\sum_{g=1}^G\left(\phi^{*g},\frac{1}{v^g}\varphi^g_{n+1}\right)$ is inherently constant \\
\end{block}

@@

%-------------------------------------------------------------------
\begin{frame}{Time Discretization}
\vspace{-3mm}

\begin{block}{Time Discretizations}
\begin{itemize}
\item Implicit Euler - 1st Order
\item Crank-Nicolson - 2nd Order
\item Backward Difference Formulae (BDF) - 1st, 2nd, 3rd, 4th Order
\item Singly-Diagonally-Implicit Runge-Kutta (SDIRK) - 3rd Order (SDIRK33)
\end{itemize}
\end{block}

\begin{block}{Time Step Adaptation}
\begin{itemize}
\item Determining appropriate time step is difficult without prior knowledge of the solution
\item Some areas of the transient may require smaller time steps for constant accuracy
\item Time adaptation predicts the local truncation error and computes a time step appropriate for a given tolerance
\item Examples:
\begin{itemize}
\item Step doubling
\item Embedded Runge-Kutta
\end{itemize}
\end{itemize}
\end{block}

@@

%-------------------------------------------------------------------
\begin{frame}{Step doubling time adaption was chosen for testing}

\begin{block}{Step Doubling Solution Process}

@@

%-------------------------------------------------------------------
\begin{frame}{Treatment of delayed neutron precursors}
\vspace{-3mm}
\begin{block}{Delayed neutron precursor equation is an ODE}
\begin{equation*}
\frac{dC_i}{dt} = \tcr{p}\sum_{g=1}^G \beta_i\nu \Sigma_f^g \tcb{\varphi^{g}} - \lambda_iC_i , \quad 1 \le i \le I
\end{equation*}
\end{block}

\begin{block}{Time Integration of Precursors}
\begin{itemize}
\item Trapezoid Rule:
\be
C^{n+1}_i = \frac{1-0.5\Delta t\lambda_i}{1+0.5\Delta t\lambda_i}C^n_i + \frac{0.5\Delta t \beta_i}{1+0.5\Delta t\lambda_i}\sum_{g=1}^G\left[(\nu\Sigma_f^g\tcb{\varphi^g})^n \tcr{p^n} +  (\nu\Sigma_f^g\tcb{\varphi^g})^{n+1} \tcr{p^{n+1}}\right]
\ee
\item Analytical Integration:
\be 
C^{n+1}_i = C^n_i e^{-\lambda_i \Delta t} + \sum_{g=1}^G\left(\hat{a}_{2,i} (\nu\Sigma_f^g\tcb{\varphi^g})^{n+1}+\hat{a}_{1,i} (\nu\Sigma_f^g\tcb{\varphi^g})^n\right)\beta_i
\ee
\vspace{-4mm}
\begin{align*}
&\hat{a}_{1,i}= \int_{t_n}^{t_{n+1}}\frac{t_{n+1}-t'}{\Delta t}\tcr{p(t')}e^{-\lambda_i(t_{n+1}-t')}dt' \\
&\hat{a}_{2,i} = \int_{t_n}^{t_{n+1}}\frac{t'-t_n}{\Delta t}\tcr{p(t')}e^{-\lambda_i(t_{n+1}-t')}dt'
\end{align*}
\end{itemize}
\end{block}

@@

%-------------------------------------------------------------------
\begin{frame}{Multiphysics: Adiabatic heat-up with absorption cross-section feedback}

\begin{block}{Implemented Form}
\be
\rho c_p \frac{\partial T(\vec{r},t)}{\partial t} = \kappa_f \sum^G_{g=1}\Sigma_f^g \tcb{\varphi^g(\vec{r},t)}\tcr{p(t)}
\ee
\be
\Sigma_a^{thermal}(\vec{r},t) = \Sigma_a^{thermal}(\vec{r},0)\left[1+\gamma\left(\sqrt{T}-\sqrt{T_0}\right)\right]
\ee
\end{block}

\begin{block}{Analytical temperature integration with IQS}
\be
T^{n+1} = T^n + \frac{\kappa_f}{\rho c_p} \sum_{g=1}^G\left(a_2(\Sigma_f^g\tcb{\varphi^g})^{n+1} + a_1(\Sigma_f^g\tcb{\varphi^g})^n\right)
\label{eq:temp_an}
\ee
\be
a_1 = \int_{t_n}^{t_{n+1}}\left(\frac{t_{n+1}-t'}{\Delta t}\right)\tcr{p(t')}dt'
\label{eq:a1}
\ee
\be
a_2 = \int_{t_n}^{t_{n+1}}\left(\frac{t'-t_n}{\Delta t}\right)\tcr{p(t')}dt'
\label{eq:a2}
\ee
\end{block}

@@

\begin{block}{Solution Methods}
\begin{multicols}{2}
\begin{enumerate}
\item Implicit Discretization
\begin{itemize}
\item Precursor variable coupling
\item Theta precursor elimination
\item Analytical precursor elimination
\end{itemize}
\item IQS
\begin{itemize}
\item Precursor variable coupling
\item Theta precursor elimination
\item Analytical precursor elimination
\end{itemize}
\item IQS P-C
\begin{itemize}
\item Theta precursor elimination
\item Analytical precursor elimination
\end{itemize}
\end{enumerate}
\end{multicols}
\end{block}

@@

%-------------------------------------------------------------------
\begin{frame}{Results}

\begin{multicols}{2}
\tableofcontents[currentsection]
\end{multicols}

@@

\begin{columns}
\column{\dimexpr\paperwidth-10pt}
\begin{figure}
\includegraphics[width=0.5\paperwidth]{figures/1D_conv_Rat.png}
\includegraphics[width=0.5\paperwidth]{figures/1D_conv_lin.png}
\end{figure}
\end{columns}

@@

%-------------------------------------------------------------------
\begin{frame}{Transient-15 Results}
\vspace{-3mm}

\begin{block}{Accuracy and Runtime}
\begin{center}
\resizebox{\linewidth}{!}{
\begin{tabular}{|l|ccc|}
\hline
Method & No. of Steps & \% Increase Runtime$^*$ & Max Power Error \\
\hline
Implicit Dis. 		& 300 &	---		&	7.875e-4	\\
IQS 				& 300 & -11.9\%	&	8.385e-5	\\
IQS (5 updates) 	& 300 &  49.7\%	&	3.687e-5	\\
IQS P-C 			& 300 &  -2.1\%	&	7.527e-4	\\
IQS P-C (5 updates) & 300 &  26.5\%	&	1.227e-4	\\
\hline
\end{tabular}
}
\end{center}
\vspace{-3mm}
$^*$ difference in runtime from implicit discretization 
\end{block}

@@

\begin{block}{IQS with Temperature Feedback}
\begin{itemize}
\item IQS was successfully implemented into the Rattlesnake/MOOSE framework
\item Added intermediate time scale loop for temperature
\item Incorporation of temperature into the quasi-static process significantly improved computational efficiency
\item Dynamical time scale analysis demonstrated proof-of-concept for variant time scales
\end{itemize}
\end{block}

@@

\begin{block}{Multiphysics}
Test IQS with other reactor physics, including:
\begin{itemize}
\item More complex temperature feedback
\item Thermal Hydraulics
\item Fuel Mechanics
\end{itemize}
\end{block}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\backupbegin
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\backupend
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
